IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-01-24 codes/R/cohorts_nc.Rnw
- add age-sex adjustment as regression - modify plots to display by gender - separate scores from graphs into different scripts - adapt tables and graphs in Rnw NOTE: text in Rnw NOT updated

<<READ, cache=FALSE >>=
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/1_load.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/2_efa.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_mifa_invariance.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_mifa_final.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_mifa_cog.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_graphs.R")

@@

                                            & $\\bm{\\lambda}$
                                            & $\\bm{\\tau}_1$
                                            & $\\bm{\\tau}_2$
                                            & $\\bm{\\nu}$ \\\\
                                            Measure & BCS = MCS
                                            & BCS = MCS
                                            & BCS = MCS
                                            & MCS (BCS=0)
                                            & Factor
                                            \\\\", sep=""))),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabularx", width = "\\textwidth",
             floating = FALSE
)

@@

print.xtable(xtable(table,
                    align = "llccc",
                    # align="L{0cm}L{.1\\textwidth}L{.2\\textwidth}L{.15\\textwidth}L{.15\\textwidth}L{.15\\textwidth}L{.15\\textwidth}",
                    digits = 3
                    ),
             size="\\small",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0,2)),
                              command = c(
                              # header
                                    paste(" & \\multicolumn{3}{c}{\\textbf{BCS}} \\\\ \\midrule
                                            & \\multicolumn{1}{c}{\\textbf{Mean}}
                                            & \\multicolumn{2}{c}{\\textbf{Covariance}} \\\\
                                            && $\\theta^{EXT}$ & $\\theta^{INT}$ \\\\", sep=""),
                                    paste(" \\midrule & \\multicolumn{3}{c}{\\textbf{MCS}} \\\\ \\midrule
                                            & \\multicolumn{1}{c}{\\textbf{Mean}}
                                            & \\multicolumn{2}{c}{\\textbf{Covariance}} \\\\
                                            && $\\theta^{EXT}$ & $\\theta^{INT}$ \\\\", sep="")
                                    )),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabularx", width = ".5\\textwidth",
             floating = FALSE
)

\begin{table}[ht]
\caption{Estimated latent variable means and covariances -- model with restricted intercepts} \label{tab:lvpars2}
\centering
<<RES_FA_LV2, dependson="FA_FINAL_PARS", results='asis'>>=
require(xtable)

table <- lvpars2

print.xtable(xtable(table,
                    align = "llccc",
                    # align="L{0cm}L{.1\\textwidth}L{.2\\textwidth}L{.15\\textwidth}L{.15\\textwidth}L{.15\\textwidth}L{.15\\textwidth}",
                    digits = 3
                    ),
             size="\\small",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0,2)),
                              command = c(
                              # header
                                    paste(" & \\multicolumn{3}{c}{\\textbf{BCS}} \\\\ \\midrule
                                            & \\multicolumn{1}{c}{\\textbf{Mean}}
                                            & \\multicolumn{2}{c}{\\textbf{Covariance}} \\\\
                                            && $\\theta^{EXT}$ & $\\theta^{INT}$ \\\\", sep=""),
                                    paste(" \\midrule & \\multicolumn{3}{c}{\\textbf{MCS}} \\\\ \\midrule
                                            & \\multicolumn{1}{c}{\\textbf{Mean}}
                                            & \\multicolumn{2}{c}{\\textbf{Covariance}} \\\\
                                            && $\\theta^{EXT}$ & $\\theta^{INT}$ \\\\", sep="")
                                    )),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabularx", width = ".5\\textwidth",
             floating = FALSE
)

@@

reg.bcs.ext <- lm(EXT~as.factor(incq), data=subset(facandraw, cohort=="BCS"))
bcs.51.ext <- round(reg.bcs.ext$coefficients["as.factor(incq)5"],2)
reg.bcs.int <- lm(INT~as.factor(incq), data=subset(facandraw, cohort=="BCS"))
bcs.51.int <- round(reg.bcs.int$coefficients["as.factor(incq)5"],2)

reg.mcs.ext <- lm(EXT~as.factor(incq), data=subset(facandraw, cohort=="MCS"))
mcs.51.ext <- round(reg.mcs.ext$coefficients["as.factor(incq)5"],2)
reg.mcs.int <- lm(INT~as.factor(incq), data=subset(facandraw, cohort=="MCS"))
mcs.51.int <- round(reg.mcs.int$coefficients["as.factor(incq)5"],2)

@@

\begin{figure}
<<FACINEQ, dev='tikz', fig.height=10, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Distribution of scores across income quintiles}\label{fig:boxscores}
{\scriptsize \emph{Notes}: The figure plots the distribution of the scored factors from model \eqref{eq:finalmod} across the quintiles in the income distribution. \par}
\end{figure}

>>>>

<<READ, cache=FALSE >>=
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/1_load.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/2_efa.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_mifa_invariance.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_mifa_final.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/5_graphs.R")

@@

                                            & $\\bm{\\lambda}$
                                            & $\\bm{\\tau}_1$
                                            & $\\bm{\\tau}_2$
                                            & $\\bm{\\varepsilon}$ \\\\
                                            Measure & BCS = MCS
                                            & BCS = MCS
                                            & BCS = MCS
                                            & MCS (BCS=1)
                                            & Factor
                                            \\\\", sep=""))),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabularx", width = "\\textwidth",
             floating = FALSE
)

@@

print.xtable(xtable(table,
                    align="L{0cm}L{.07\\textwidth}C{.07\\textwidth}C{.07\\textwidth}C{.07\\textwidth}C{.07\\textwidth}C{.07\\textwidth}C{.07\\textwidth}C{.07\\textwidth}C{.07\\textwidth}",
                    digits = 3
                    ),
             size="\\small",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0)),
                              command = c(
                              # header
                                    paste(" & \\multicolumn{4}{c}{\\textbf{BCS}}
                                            & \\multicolumn{4}{c}{\\textbf{MCS}} \\\\ \\cmidrule(lr){2-5} \\cmidrule(lr){6-9}
                                            & Mean & \\multicolumn{2}{c}{Covariance} & Corr. & Mean & \\multicolumn{2}{c}{Covariance} & Corr. \\\\
                                            ", sep="")
                                    )),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabularx", width = ".85\\textwidth",
             floating = FALSE
)

@@

reg.bcs.ext <- lm(EXT~as.factor(incq) + age, data=subset(items.scored, cohort=="BCS"))
bcs.51.ext <- round(reg.bcs.ext$coefficients["as.factor(incq)5"],2)
reg.bcs.int <- lm(INT~as.factor(incq) + age, data=subset(items.scored, cohort=="BCS"))
bcs.51.int <- round(reg.bcs.int$coefficients["as.factor(incq)5"],2)

reg.mcs.ext <- lm(EXT~as.factor(incq) + age, data=subset(items.scored, cohort=="MCS"))
mcs.51.ext <- round(reg.mcs.ext$coefficients["as.factor(incq)5"],2)
reg.mcs.int <- lm(INT~as.factor(incq) + age, data=subset(items.scored, cohort=="MCS"))
mcs.51.int <- round(reg.mcs.int$coefficients["as.factor(incq)5"],2)

@@

\begin{figure}
<<FACINEQ, dev='tikz', fig.height=12, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Distribution of scores across income quintiles}\label{fig:boxscores}
{\scriptsize \emph{Notes}: The figure plots the distribution of the scored factors from model \eqref{eq:finalmod} across the quintiles in the income distribution. \par}
\end{figure}
